404 -- Page Not Found   

### 2025-03-24 IndividualStudies/DH_2017.qmd
adding a draft of the NAPE page

Depicted below are the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA.

@@

```{r Making Heat Map, echo=FALSE, fig.height=10, warning=FALSE}

@@

```{r Making Venn Diagram, echo=FALSE, warning=FALSE, width = 8}

@@

<iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>
:::

>>>>

@@

```{r Making Heat Map, echo=FALSE, fig.height=10, warning=FALSE}
#| fig-cap: "Heat map depicts the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA. Color denotes the "

@@

```{r Making Venn Diagram, echo=FALSE, warning=FALSE, width = 8}
#| fig-cap: "A Venn diagram depicts the overlapping identification of proteins between the three lipid probes. There are 41 proteins uniquely identified after enrichment with tf-Sph, 130 proteins uniquely identified after enrichment with tf-DAG, and no proteins uniquely identified to tf-8:3-FA."

@@

<iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>

### 2025-03-24 StudyInformation_includes/AT_2025_include.qmd
adding a draft of the NAPE page

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PA.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidylethanolamine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
</span>

>>>>

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Trifunctional Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PA.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Trifunctional Phosphatidylethanolamine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
</span>

### 2025-03-24 StudyInformation_includes/DH_2017_include.qmd
Trying to fix the dotplot framing on mobile, not much luck yet
adding a draft of the NAPE page

[Sphingosine](/LipidProbe/Sphingosine.qmd)

[Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)

[8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)

@@

>>>>

[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)

[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)

[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)

@@

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| Sph |  5 min | 2.5 min  | 0 min | 2.5 min  |
| DAG |  15 min | 2.5 min  | 0 min | 2.5 min  |
| 8-3 FA |  15 min | 2.5 min  | 0 min | 2.5 min  |
